Time Series Modeling of Varying Complexity Captures Subdiffusive Solute Dynamics and Predicts Long Timescale Behavior in Nanoscale Pores.

### 2019-11-25 Ben_Manuscripts/stochastic_transport/Draft.tex
Updated parameters. New plots

  We used the mean first passage time (MFPT) in order to quantify how long it would take a 
  typical particle, parameterized with the above models, to travel across a membrane pore
  of length $L$. To measure this quantity, we simulated realizations of 10000 particle 
  trajectories, started at the pore entrance ($z=0$). In the case of uncorrelated hops, one
  can continuously draw from the hop length distribution until $z \geq L$ (Or $-L$ for 
  the sake of computational efficiency). The length of time between the last time the 
  particle crossed $z=0$ and the end of the trajectory gives a single passage time. 
  When particle hops are correlated, as they are in all cases of this work, we cannot 
  continuously construct the particle trajectories. Rather, we must generate trajectories
  of length $n$ and measure the length of the sub-trajectory which traverses from $0$ 
  to $L$ without becoming negative. It is important to choose a value of $n$ sufficiently
  large that all trajectories reach $L$, or else the mean first passage time will 
  be underestimated.

  Our definition of the mean first passage time differs from more standard treatments.
  The setup of our system is consistent with a one dimensional interval with two absorbing 
  boundaries. In the absence of an external force and a constant diffusion coefficient, $D$, 
  the mean first passage time is simply:
  \begin{equation}
  T = \frac{z_0(L - z_0)}{2D}
  \end{equation}
  where $z_0$ is the initial position of particle trajectories.~\cite{gitterman_mean_2000}
  Of course that implies a conventional MFPT of 0 since particles overwhelmingly exit the
  pore at $z=0$. Therefore, we chose only to include trajectories in the MFPT calculation 
  which cross the boundary at $L$. We are unaware of an analytical form of the MFPT or 
  the distribution of passage times describing our system even in the simplest case of 
  Brownian increments.

  In the absence of an analytical equation for the MFPT, we instead report the location of
  the peak of the passage time distribution. This has the added advantage of treating
  cases where the passage time distribution diverges and no mean exists. While we will
  call the peak in the distribution the MFPT, it is important to recognize that this 
  value is more representative of a typical passage time rather than a mean.

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  The parameter estimates describing our 1 and 2 mode models are summarized in 
  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}.

@@

@@

  %MRS4: might this work better visually?  Table in SI, figure here?
  %BJC4: Are you talking about the table after this figure? Somehow I'd need to fit 108 pieces of data into a single figure
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) Emission distributions are non-Gaussian and heavy-tailed. Shown here is the
  emission distribution for transitions between states. The maximum likelihood
  Gaussian fit severely underestimates the empirical density of hops near and far from zero 
  while overestimating the density of hops at intermediate values. (b) Jumps drawn from
  the transition distribution are negatively correlated to each other. The normalized version 
  of Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
  an appropriate way to model jumps.} \label{fig:msddm_emissions}
  \end{figure}

  \begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
  State & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$   & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$ \\\hline
  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045      & 0.11  & 1.56     & 0.052    & 0.10 & 1.78     & 0.035    \\
  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037      & 0.07  & 1.63     & 0.043    & 0.08 & 1.88     & 0.032    \\
  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030      & 0.02  & 1.80     & 0.036    & 0.04 & 2.00     & 0.030    \\
  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028      & 0.02  & 1.75     & 0.036    & 0.04 & 2.00     & 0.027    \\
  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062      & 0.10  & 1.28     & 0.074    & 0.13 & 1.47     & 0.048    \\
  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040      & 0.03  & 1.50     & 0.042    & 0.09 & 1.70     & 0.038    \\
  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040      & 0.28  & 1.20     & 0.043    & 0.08 & 1.77     & 0.031    \\
  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030      & 0.04  & 1.83     & 0.037    & 0.01 & 2.00     & 0.030    \\
  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045      & 0.35  & 1.45     & 0.057    & 0.34 & 1.54     & 0.040    \\\hline
  \end{tabular}
  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
  trajectories and used them to generate realizations of our MSDDM model. The states
  are defined in Table~\ref{table:states} except state T which describes the transition
  emissions.}\label{table:msddm_params}
  \end{table}
%  
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
%  \hline
%  & \multicolumn{4}{c|}{Urea}                      & \multicolumn{4}{c|}{Ethylene Glycol} \\\hline
%  State & H     & $\alpha_h$ & $\sigma$ & $T_{ii}$ & H    & $\alpha_h$ & $\sigma$ & $T_{ii}$  \\\hline
%  1     & 0.10  & 1.79       & 0.034    &  0.60    & 0.09 & 1.68       & 0.045    & 0.41 \\
%  2     & 0.06  & 1.80       & 0.033    &  0.38    & 0.09 & 1.75       & 0.037    & 0.58 \\
%  3     & 0.11  & 1.88       & 0.030    &  0.73    & 0.11 & 1.86       & 0.030    & 0.21 \\
%  4     & 0.10  & 1.95       & 0.027    &  0.57    & 0.04 & 1.91       & 0.028    & 0.34 \\
%  5     & 0.19  & 1.34       & 0.048    &  0.62    & 0.15 & 1.40       & 0.062    & 0.47 \\
%  6     & 0.15  & 1.45       & 0.040    &  0.38    & 0.11 & 1.52       & 0.040    & 0.62 \\
%  7     & 0.15  & 1.61       & 0.032    &  0.61    & 0.05 & 1.60       & 0.040    & 0.15 \\
%  8     & 0.11  & 1.71       & 0.028    &  0.41    & 0.05 & 1.74       & 0.030    & 0.29 \\
%  T     & 0.34  & 1.42       & 0.036    &   --     & 0.37 & 1.44       & 0.045    &  --  \\\hline
%  \end{tabular}
%  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
%  trajectories and then computed the average ensemble-averaged MSD of 10000 
%  simulated trajectories. The states are defined in Table~\ref{table:states}
%  except state T which refers to the transition emissions.}\label{table:msddm_params}
%  \end{table}

@@

  % /figures/msddm_state_probabilities.py
  \begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{state_probabilities.pdf}
  \caption{The probability of finding urea or ethylene glycol in a given state.}\label{fig:state_probabilities}
  \end{figure}

@@

  In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
  with pore length. We fit a curve of the form $cL^{\alpha}$ to the curves in order
  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
  to the solute MSDs which is consistent with longer passage times for solutes that
  progres through the pores more slowly.

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
  \caption{}\label{fig:mfpt_curves_regular}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
  \caption{}\label{fig:mfpt_curves_brownian}
  \end{subfigure}
  \caption{}\label{fig:mfpt_curves}
  \end{figure}

  The growth exponent is inversely related to the hurst parameter. In 
  Figure~\ref{fig:mfpt_curves_brownian}, we removed the correlation structure (set
  $H$=0.5) from AD trajectory realizations so that all hops were uncorrelated.
  Regardless of the parameters of the dwell time distribution, the growth 
  exponent is always about 2, the same value that we observe for Brownian 
  motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the Supporting 
  Information).

  Comparison of Figures~\ref{fig:mfpt_curves_regular} and~\ref{fig:mfpt_curves_brownian}
  highlights that the Hurst parameter plays a major role in

  The correlation between hops signficantly

>>>>

  We used the mean first passage time (MFPT) in order to quantify how long it would take a 
  typical particle, parameterized with the above models, to travel across a membrane pore
  of length $L$. To measure this quantity, we simulated 50000 realizations of particle 
  trajectories, released at the pore entrance ($z=0$). In the case of uncorrelated hops, one
  can continuously draw from the hop length distribution until $z \geq L$ (or $-L$ for 
  the sake of computational efficiency). The length of time between the last time the 
  particle crossed $z=0$ and the end of the trajectory gives a single passage time. 
  When particle hops are correlated, as they are in all cases of this work, we cannot 
  continuously construct the particle trajectories. Rather, we must generate trajectories
  of length $n$ and measure the length of the sub-trajectory which traverses from $0$ 
  to $L$ without becoming negative.
  %BJC4: below is only necessary if you the mean of the distribution exists.
  %It is important to choose a value of $n$ sufficiently
  %large that all trajectories reach $L$, or else the mean first passage time will 
  %be underestimated.

  Our definition of the MFPT differs from more standard treatments. The setup of our 
  system is consistent with a one dimensional interval with two absorbing boundaries. In
  the absence of an external force and with a constant diffusion coefficient,
  $D$, the MFPT is simply:
  \begin{equation}
  T = \frac{z_0(L - z_0)}{2D}
  \end{equation}
  where $z_0$ is the initial position of particle trajectories.~\cite{gitterman_mean_2000}
  Of course that implies a conventional MFPT of 0 since particles overwhelmingly exit the
  pore at $z=0$. Therefore, we chose only to include trajectories in the MFPT calculation 
  which cross the boundary at $L$. We are unaware of an analytical form of the MFPT or 
  the distribution of passage times describing our system even in the simplest case of 
  Brownian increments. %BJC4: still digging for an analytical solution. Rich said the 
  %'marathon' runner problem might give a solution. It may be the same as the distribution
  % of runners crossing the finish line

  %BJC4: I'm not sure the best way to get the peak
  In the absence of an analytical equation for the MFPT, we instead report the location of
  the peak of the passage time distribution. This has the added advantage of treating
  cases where the passage time distribution diverges and no mean exists. While we will
  call the peak in the distribution the MFPT, it is important to recognize that this 
  value is more representative of a typical passage time rather than a mean.

@@

  The evidence suggests that solutes in this system can be well-modeled by subordinated
  fractional Brownian motion. The solutes clearly perform jumps after periods of relative
  immobility (see Figure~\ref{fig:solute_trajectories} for example). The near-Gaussian distribution
  of jump lengths and power law distribution of dwell times are both characteristic of 
  CTRWs (Figures~\ref{fig:hop_distribution_comparison} and~\ref{fig:powerlaw}). The apparent
  anti-correlation between hops suggests a fractional diffusion process is subordinate to the
  CTRW. We believe the subordinated process is FBM because its analytical correlation 
  structure is close to that observed in our simulation (Figure~\ref{fig:hop_acf}). FBM
  is common in crowded viscoelastic environments where motions are highly influenced by
  the motion of surrounding components, such as monomer tails in our case.~\cite{ernst_fractional_2012}
  The parameter estimates describing our 1 and 2 mode models are summarized in 
  Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode} (also trying it out in 
  Figures~\ref{fig:radars} and~\ref{fig:radars_nolines})

@@

  %BJC4: another way to visualize data
  %BJC4: I think these are kind of hard to read. Can't really see any trends. Open to other
  %ideas.
  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{1mode_radar.pdf}
  \caption{}\label{fig:1mode_radar}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{2mode_radar.pdf}
  \caption{}\label{fig:2mode_radar}
  \end{subfigure}
  \caption{Another way to visualize Tables~\ref{table:sfbm_params} and~\ref{table:sfbm_params_2mode}}\label{fig:radars}
  \end{figure}

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
  \caption{}\label{fig:1mode_radar}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\linewidth]{2mode_radar_nolines.png}   % for some reason it has trouble saving this as a PDF
  \caption{}\label{fig:2mode_radar}
  \end{subfigure}
  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
  \end{figure}

%  \begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\linewidth]{1mode_radar_nolines.pdf}
%  \caption{}\label{fig:1mode_radar_nolines}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\linewidth]{2mode_radar_nolines.pdf}
%  \caption{}\label{fig:2mode_radar_nolines}
%  \end{subfigure}
%  \caption{Same as Figure~\ref{fig:radars} but with no lines between points}\label{fig:radars_nolines}
%  \end{figure}

@@

  %MRS4: might this work better visually?  Table in SI, figure here?
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{gaussian_levy_comparison.pdf}
  \caption{}\label{fig:gaussian_levy_comparison}
  \end{subfigure}
  % /figures/msddm_acf.py
  \begin{subfigure}{0.42\textwidth}
  \includegraphics[width=\textwidth]{msddm_acf.pdf}
  \caption{}\label{fig:msddm_acf}
  \end{subfigure}
  \caption{(a) Emission distributions are non-Gaussian and heavy-tailed. Shown here is the
  emission distribution for transitions between states. The maximum likelihood
  Gaussian fit severely underestimates the empirical density of hops near and far from zero 
  while overestimating the density of hops at intermediate values. (b) Jumps drawn from
  the transition distribution are negatively correlated to each other. The normalized version 
  of Equation~\ref{eqn:flm_autocovariance} fits well to the data suggesting FLM is
  an appropriate way to model jumps.} \label{fig:msddm_emissions}
  \end{figure}

  \begin{table}[h]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|c|c|c|}
  \hline
  & \multicolumn{3}{c|}{Urea} & \multicolumn{3}{c|}{Ethylene Glycol} & \multicolumn{3}{c|}{Methanol} & \multicolumn{3}{c|}{Acetic Acid} \\\hline
  State & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$   & H     &$\alpha_h$& $\sigma$ & H    &$\alpha_h$& $\sigma$ \\\hline
  1     & 0.10  & 1.79     & 0.034    & 0.09 & 1.68     & 0.045      & 0.11  & 1.56     & 0.052    & 0.10 & 1.78     & 0.035    \\
  2     & 0.06  & 1.80     & 0.033    & 0.09 & 1.75     & 0.037      & 0.07  & 1.63     & 0.043    & 0.08 & 1.88     & 0.032    \\
  3     & 0.11  & 1.88     & 0.030    & 0.11 & 1.86     & 0.030      & 0.02  & 1.80     & 0.036    & 0.04 & 2.00     & 0.030    \\
  4     & 0.10  & 1.95     & 0.027    & 0.04 & 1.91     & 0.028      & 0.02  & 1.75     & 0.036    & 0.04 & 2.00     & 0.027    \\
  5     & 0.19  & 1.34     & 0.048    & 0.15 & 1.40     & 0.062      & 0.10  & 1.28     & 0.074    & 0.13 & 1.47     & 0.048    \\
  6     & 0.15  & 1.45     & 0.040    & 0.11 & 1.52     & 0.040      & 0.03  & 1.50     & 0.042    & 0.09 & 1.70     & 0.038    \\
  7     & 0.15  & 1.61     & 0.032    & 0.05 & 1.60     & 0.040      & 0.28  & 1.20     & 0.043    & 0.08 & 1.77     & 0.031    \\
  8     & 0.11  & 1.71     & 0.028    & 0.05 & 1.74     & 0.030      & 0.04  & 1.83     & 0.037    & 0.01 & 2.00     & 0.030    \\
  T     & 0.34  & 1.42     & 0.036    & 0.37 & 1.44     & 0.045      & 0.35  & 1.45     & 0.057    & 0.34 & 1.54     & 0.040    \\\hline
  \end{tabular}
  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
  trajectories and used them to generate realizations of our MSDDM model. The states
  are defined in Table~\ref{table:states} except state T which describes the transition
  emissions.}\label{table:msddm_params}
  \end{table}

  %BJC4: better visualization scheme
  \begin{figure}
  \centering
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{H_v_state.pdf}
  \caption{}\label{fig:H_v_state}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{alpha_v_state.pdf}
  \caption{}\label{fig:alpha_v_state}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{sigma_v_state.pdf}
  \caption{}\label{fig:sigma_v_state}
  \end{subfigure}
  \begin{subfigure}{0.49\textwidth}
  \includegraphics[width=\textwidth]{state_probabilities.pdf}
  \caption{}\label{fig:state_probabilities}
  \end{subfigure}
  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
  trajectories and used them to generate realizations of our MSDDM model. The states
  are defined in Table~\ref{table:states} except state T which describes the transition
  emissions.}\label{fig:msddm_parameters}
  \end{figure}

%  
%  \begin{table}[h]
%  \centering
%  \begin{tabular}{|c|c|c|c|c|c|c|c|c|}
%  \hline
%  & \multicolumn{4}{c|}{Urea}                      & \multicolumn{4}{c|}{Ethylene Glycol} \\\hline
%  State & H     & $\alpha_h$ & $\sigma$ & $T_{ii}$ & H    & $\alpha_h$ & $\sigma$ & $T_{ii}$  \\\hline
%  1     & 0.10  & 1.79       & 0.034    &  0.60    & 0.09 & 1.68       & 0.045    & 0.41 \\
%  2     & 0.06  & 1.80       & 0.033    &  0.38    & 0.09 & 1.75       & 0.037    & 0.58 \\
%  3     & 0.11  & 1.88       & 0.030    &  0.73    & 0.11 & 1.86       & 0.030    & 0.21 \\
%  4     & 0.10  & 1.95       & 0.027    &  0.57    & 0.04 & 1.91       & 0.028    & 0.34 \\
%  5     & 0.19  & 1.34       & 0.048    &  0.62    & 0.15 & 1.40       & 0.062    & 0.47 \\
%  6     & 0.15  & 1.45       & 0.040    &  0.38    & 0.11 & 1.52       & 0.040    & 0.62 \\
%  7     & 0.15  & 1.61       & 0.032    &  0.61    & 0.05 & 1.60       & 0.040    & 0.15 \\
%  8     & 0.11  & 1.71       & 0.028    &  0.41    & 0.05 & 1.74       & 0.030    & 0.29 \\
%  T     & 0.34  & 1.42       & 0.036    &   --     & 0.37 & 1.44       & 0.045    &  --  \\\hline
%  \end{tabular}
%  \caption{We calculated values of $H$, $\alpha_h$ and $\sigma$ from MD simulation
%  trajectories and then computed the average ensemble-averaged MSD of 10000 
%  simulated trajectories. The states are defined in Table~\ref{table:states}
%  except state T which refers to the transition emissions.}\label{table:msddm_params}
%  \end{table}

@@

  % /figures/msddm_state_probabilities.py
  %BJC4: combined with previous figure.
%  \begin{figure}
%  \centering
%  \includegraphics[width=0.5\textwidth]{state_probabilities.pdf}
%  \caption{The probability of finding urea or ethylene glycol in a given state.}\label{fig:state_probabilities}
%  \end{figure}
%

@@

  In Figure~\ref{fig:mfpt_curves_regular} we show that the MFPT grows super-linearly
  with pore length. We fit a curve of the form $cL^{\alpha}$ to the curves in order
  to estimate the growth exponent, $\alpha$. The growth exponent is inversely proportional
  to the solute MSDs which is consistent with longer passage times for solutes that
  progress through the pores more slowly.

  The growth exponent is inversely related to the hurst parameter, $H$. In 
  Figure~\ref{fig:mfpt_curves_brownian}, we removed the correlation structure (set
  $H$=0.5) from AD trajectory realizations so that all hops were uncorrelated.
  Regardless of the parameters of the dwell time distribution, the growth 
  exponent is always about 2, the same value that we observe for Brownian 
  motion (see Figure~\ref{S-fig:mfpt_curve_brownian} of the Supporting 
  Information).

  % BJC5: I'm not sure the best way to calculate statistics on this. Since I don't know
  % the density function of the mean first passage time distribution, I use bins to 
  % to locate the peaks. So the error bars are dependent on the bin width. 
  \begin{figure}
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{mfpt_curves.pdf}
  \caption{Correlated Hops}\label{fig:mfpt_curves_regular}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{mfpt_curves_brownian.pdf}
  \caption{Uncorrelated Hops}\label{fig:mfpt_curves_brownian}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{frac_pore.pdf}  % This figure might fit in earlier
  \caption{}\label{fig:frac_pore}
  \end{subfigure}
  \caption{(a) We fit the MFPT versus pore length to a function of the form $cL^{\alpha}$. 
  The MFPT grows super-linearly with increasing pore length. Solutes with lower MSDs have
  higher MFPTs. (b) If we remove correlation between hops, the MFPTs reduce significantly
  and the growth exponent stays constant at 2 for all solutes independent of dwell
  distribution parameters. Higher degrees of anti-correlation (lower $H$) lead to higher
  growth exponents. (c) Solutes that spend a large fraction of their time in the tails tend
  to have larger Hurst parameters.}\label{fig:mfpt_curves}
  \end{figure}

  Comparison of Figures~\ref{fig:mfpt_curves_regular} and~\ref{fig:mfpt_curves_brownian}
  highlights that anti-correlation between hops plays a major role in solute passage times.
  With a pore length of 50 nm, the MFPT of the fasted moving solute, ethylene glycol is 
  c.a. 5 times higher with versus without anti-correlated hops. The MFPTs of the slowest
  moving solute, acetic acid, are about 16 times higher by the same comparison. This 
  difference will only grow with increasing pore length.

  In Figure~\ref{fig:frac_pore}, we show that solutes which spend more time in the tails
  tend to have lower Hurst parameters. The densely packed, viscoelastic alkane chains 
  bounce solutes between them, severely limiting their mobility. Designing LLC membranes
  that can control or prevent the partition of solutes into the tails may offer the highest
  returns on membrane performance.
